**Pre-prints**

### 2016-12-06 submission/Schloss_PrePrints_mBio_2017.Rmd
Outline paper

@@

## Introduction

>>>>

## Importance

@@

## Introduction
* Better represents the scientific method
* ASM Policies towards Pre-prints
	* Bring 'em on
	* Citable
	* Direct submission
	* mSphereDirect

## Critiques
* Half-baked science
	* Sure. What's your point
	* Post-publication peer review
* Will get scooped
	* No, PP establish priority

## Pre-print host landscape
* Review different sites
* Licensing
* Cost
* Opportunity for comments

## Pre-prints in microbiology
* Rate of use among PP describing microbiology research over time
* Number of revisions
* Number of downloads
* Number of PP published

## Anecdotes
* MinIon methods
* PacBio paper
* Tardigrade microbiome
* NYC subway microbiome

## References
